Current and future constraints on primordial magnetic fields

### 2017-01-30 pmf.tex
beam section

\begin{figure}[htb]\centering
\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
  \caption[]{ \label{fig:beam}
 Larger telescopes (and smaller beams) will improve limits on the PMF power. 
 Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
    }
\end{figure}

Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered.
 A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales.

>>>>

\begin{figure}[htb]\centering
\includegraphics[width=0.45\textwidth,clip,trim={1.5cm 12.5cm 11cm 7.5cm}]{pmf_beam.pdf}
  \caption[]{ \label{fig:beam}
 Larger telescopes (and smaller beams) will improve limits on the PMF power. 
 Forecasts are shown for each of the three PMF scalar indices: $n_B = -2.9$ (solid), -1 (dashed), and +2 (dash-dot). 
  The black lines are for the conservative 11-parameter model, while the blue lines are for the simple \lcdm{}+\apmf{} model. 
  The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant. 
  The plateau near 4$^\prime$ for $n_B=-1, +2$ is where the gain from the $\ell\sim3000$ peak is saturated, but the resolution isn't yet adequate to pick up the next peak at $\ell > 8000$ (see  Fig.~\ref{fig:pmf-nb}).  
    }
\end{figure}

Larger telescopes will allow CMB polarization to be measured on smaller angular scales, and should therefore always improve the PMF constraints. 
As shown in Fig.~\ref{fig:beam}, we find the gains due to resolution at fixed mapping speed to be substantial for all three power law indices considered. 
We find a local plateau between FWHMs of 4$^\prime$ to 6$^\prime$; improving the angular resolution in this range does not aid PMF searches. 
We can understand this plateau by looking on the predicted PMF power in Fig.~\ref{fig:pmf-nb}. 
All three templates have two peaks across this range of angular multiples, and we would expect such a plateau when, for instance, the resolution is adequate to resolve the first peak, but not yet sufficient to resolve the second peak. 
The observed plateau positions are consistent with this hypothesis. 
 A beam size of FWHM=1$^\prime$ instead of 10$^\prime$ reduces the expected upper limit five-fold for $n_b=-2.9$ and 30- to 35-fold for the steeper PMF indices which are more heavily weighted towards small angular scales. 
   The model only matters in the nearly-scale invariant PMF case ($n_B=-2.9$), where the information on large angular scales dominates and the telescope size is relatively unimportant.
